Reading Notes

### 2020-08-11 2pd.tex
couple comments

\section*{Preliminary Work}
<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>

>>>>

\section*{Preliminary Work}
% With lan - About excitonic splitting, using DFT, DNA. 
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
% With us - Perspective paper about all things

<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
<atom typing is a pain and doing it manually is bad cite foyer paper>
